\section{Survey of Quantitative Methods}
 The bread and butter of quantitative consulting is the ability to apply quantitative methods to business problems in order to obtain actionable insight. Clearly, it is impossible (and perhaps inadvisable, in a more general sense) for any given individual to have expertise in every field of mathematics, statistics, and computer science. \par We believe that the best consulting framework is reached when a small team of consultants possesses expertise in 2 or 3 areas, as well as a decent understanding of related disciplines, and a passing knowledge in a variety of other domains: this includes keeping up with trends, implementing knowledge redundancies on the team, being conversant in non-expertise areas, and knowing where to find detailed information (online, in books, or through external resources). \newl In this section, we present an introduction for 9 ``domains'' of quantitative analysis:
\begin{itemize}[noitemsep]
\item survey sampling and data collection;
\item data processing;
\item data visualisation;
\item statistical methods;
\item queueing models;
\item data science and machine learning;
\item simulations;
\item optimisation, and
\item trend extraction and forecasting;
\end{itemize}
Strictly speaking, the domains are not free of overlaps. Large swaths of data science and time series analysis methods are quite simply statistical in nature, and it's not unusual to view optimisation methods and queueing models as sub-disciplines of operations research. Other topics could also have been included (such as Bayesian data analysis or signal processing, to name but two), and might find their way into a second edition of this book. 
\par Our treatment of these topics, by design, is brief and incomplete. Each module is directed at students who have a background in other quantitative methods, but not necessarily in the topic under consideration. Our goal is to provide a quick ``reference map'' of the field, together with a general idea of its challenges and common traps, in order to highlight opportunities for application in a consulting context. These subsections are emphatically NOT meant as comprehensive surveys: they focus on the basics and talking points; perhaps more importantly, a copious number of references are also provided. \par We will complement each section with projects projects we have tackled in our own practices. These case studies are accompanied by (partial) deliverables in the form of charts, write-ups, report extract, etc.). 
\begin{center}
    \rule{0.5\textwidth}{.4pt}
\end{center}
As a final note, we would like to stress the following: it is \textbf{IMPERATIVE} that quantitative consultants remember that acceptable business solutions are not always optimal theoretical solutions. Rigour, while encouraged, often must take a backseat to applicability. This lesson can be difficult to accept, and has been the downfall of many a promising candidate.  
%\subsection{Motivating Examples}
%\begin{itemize}
%\item Various federal departments are looking to produce national and sub-national estimates for a number of vehicle-use statistics (vehicle-km traveled, fuel consumption, idling time, etc.). What's the best way to obtain these estimates?  
%\item The \textit{National Collision Database} contains information about motorists and pedestrians involved in collisions in Canada, as well as information about the collision itself. In a fatal collision, the blood alcohol content levels cannot be obtained until after the coroner's report is available, which can take up to a year. Can we predict the missing BAC in the meantime?    
%\item The \textit{Ottawa Professional Fire Fighters Association} represents the interests of fire fighters in the City, which is pushing to reduce the number of sick leave hours to a pre-determined benchmark. Is this plan attainable? Similarly, the city has requested that three hours of training must be scheduled and logged into a computer for each twenty-four hour shift. While there is some evidence that employees are participating in increased amounts of training, the \textit{Record Management System} (RMS) suggests that such training experience is in fact decreasing. Can we determine if there are errors in the RMS numbers, or if the evidence is biased?
%\item \textit{Global Affairs Canada} (GAC) uses various tools to track the time required by employees to perform consular tasks abroad. This data stretches back over approximately twenty years. This system, and the data it collects, are used to determine the effectiveness of mission consular programs, identify weaknesses to be resolved through HR, training and other solutions, and is used to evaluate the need for resources in missions. It is in fact the pivotal element when determining whether to staff, delete, or create positions. The software is in the process of being updated/replaced. As part of this process, GAC is generating software requirements to ensure that the updated system collects accurate and relevant data, while continuing to carry out data analyses that support mission resource use management. In preparation for this update,  GAC would like to know how to implement a data collection system that will collect accurate, usable data that allows for resource use evaluation on a mission by mission basis; what data collection functionality would be required to support the use of more advanced data analysis and modeling techniques; which collected mission attributes allow for accurate assessments of missions resource use; which missions can be appropriately grouped together when evaluating mission effectiveness and efficiency (`apples to apples' comparisons). Is this feasible? 
%\item STO UNION
%\item CCNM
%\item Repable
%\item PHAC - CIS
%\item PHAC - other
%\item Nordicity
%\item CATSA - DEA
%\item CATSA - Association Rules
%\item CATSA - Queueing
%\item NWMO
%\item UWCC
%\item WBNP
%\item Bayne Sellar Boxall
%\item CAZA
%\item CMHC
%\item Commission for Public Complaints against the RCMP
%\item CRCC
%\item Synchro Canada
%\item TC - Multimodal
%\item Corrections Canada
%\item Foodicus
%\end{itemize}

%\newpage\input{sections/sub_Data_Collection.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{1}
\newpage\input{sections/sub_Data_Preparation.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{2}
%\newpage\input{sections/sub_Data_Visualisation.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{3}
%\newpage\input{sections/sub_Statistical_Analysis.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{4}
%\newpage\input{sections/sub_Queueing_Models.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{5}
%\newpage\input{sections/sub_DS_ML.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{6}
%\newpage\input{sections/sub_Simulations.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{7}
%\newpage\input{sections/sub_Optimisation.tex}\afterpage{\FloatBarrier}
%\addtocounter{subsection}{8}
%\newpage\input{sections/sub_Time_Series_and_Forecasting.tex}\afterpage{\FloatBarrier}





